Embedding Dimension of Polyhedral Losses

### 2020-06-19 colt-20/embed-dim.tex
Camera ready?

%\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\begin{restatable}{proposition}{orderableiffpath} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} iff its intersection graph is a path, i.e. a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
  \discuss{Bo in FIXME: ``Proposition 10: why is the incorrect 'definition' of path still there?''}\discuss{Jessie-Added: and two nodes have degree one}
\end{restatable}

@@

We summarize the above results in the following theorem, together with one additional result, whose proof is in Appendix~\ref{app:1-dim}: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
(See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
\begin{theorem} \label{thm:1d-tfae}
  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
  The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
\end{theorem}
\jessiet{If I understand correctly, different orderings of the reports may yield different embeddings, and these different embeddings should elicit different properties.  How to we reconcile this in the theorem statement?  Or where am I wrong?}
\raft{I think you are right, but I don't see a contradiction (do you?)}

@@

%% Bo: I think we can get away with no summary at the end.
%\paragraph{Conclusion.}
%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
%
\newpage
% Acknowledgments---Will not appear in anonymized version
\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant No.\ DGE 1650115.  This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.  We also thank Peter Bartlett, Nishant Mehta, and Hari Ramaswamy for helpful comments.  \raf{Others...?} \bo{Others...?} \jessie{Others...?}}

>>>>

%\usetikzlibrary{calc}
\newcommand{\Comments}{0}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
	\todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{green}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{purple}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{purple!20!white}{JF: #1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{orange!20!white}{BTW: #1}}
\newcommand{\discuss}[1]{\mytodo{cyan!20!white}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
\setlength{\marginparwidth}{1in}
\fi

@@

\begin{restatable}{proposition}{orderableiffpath} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} iff its intersection graph is a path, i.e. a connected graph where two nodes have degree $1$ and every other node has degree $2$.% neighbors, and two nodes have degree one.
\end{restatable}

@@

We summarize the above results in the following theorem, together with one additional result, whose proof is in Appendix~\ref{app:1-dim}: if $\ell$ has any calibrated convex surrogate at all, it must have a polyhedral one.
(See Conjecture~\ref{conj:embed-equals-ccdim} regarding higher dimensional generalizations.)
\begin{theorem} \label{thm:1d-tfae}
  Let $\ell$ be a discrete loss eliciting a finite property $\gamma$.
  The following are equivalent: (1) $\gamma$ is orderable; (2) the intersection graph of $\gamma$ is a path; (3) the two conditions of Theorem \ref{thm:construct-1d-loss} are satisfied; (4) $\ell$ is $1$-embeddable; (5) $\ell$ has some polyhedral calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$; (6) $\ell$ has some convex calibrated surrogate loss $L: \reals \to \nonnegreals^{\Y}$.
\end{theorem}
\jessiet{If I understand correctly, different orderings of the reports may yield different embeddings, and these different embeddings should elicit different properties.  How to we reconcile this in the theorem statement?  Or where am I wrong?}
\raft{I think you are right, but I don't see a contradiction (do you?)}
\jessiet{I just wanted to make sure that it was clear that we get different surrogates with different orderings, although those would elicit different properties, so I see why it's fine.}

@@

%% Bo: I think we can get away with no summary at the end.
%\paragraph{Conclusion.}
%\jessie{Not a fan, but a placeholder if we get too close to deadline.}
%In this paper, we present the notion of \emph{embedding dimension} in order to measure the efficiency of a surrogate loss function.
%While similar notions of surrogate efficiency have been studied before, we propose a characterization in $1$ dimension that generalizes to the construction of any calibrated convex surrogate.
%In higher dimensions, our characterization can only be applied to understanding the minimal dimension of a calibrated \emph{polyhedral} surrogate, although we conjecture that embedding dimension is equal to convex calibration dimension in general.
%In order to demonstrate our characterizations, we show an improved lower bound from previous work on the convex calibration dimension of $\abstain{\alpha}$, and a new lower bound on embedding dimension of $\abstain{1/2}$.
%
\newpage
% Acknowledgments---Will not appear in anonymized version
\acks{Jessie Finocchiaro was funded by NSF Graduate Research Fellowship under grant No.\ DGE 1650115.  This material is based upon work supported by the National Science Foundation under Grant No.\ 1657598.  We also thank Peter Bartlett, Nishant Mehta, and Hari Ramaswamy for helpful comments.}
